Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-07-16 ch04-lrmhinf/lrmhinf.tex
Change spacing around headings, epigraphs, ...

\begin{remark}
The notions $\svdMax{\Delta_{\LMM}(\omega)}$ and the ensuing  $\widehat{\phantom{_\infty}\infnorm{\Delta_{\LMM}}}$  should be regarded as notational convenience to denote that local models are used to estimate the maximal singular value and $\Hinf{}$ norm, respectively.
In reality, there is no tangible `$\Delta_{\LMM}$' that is constructed: neighboring local models are stitched together using the `$\max$' operator.
\end{remark}

>>>>

\begin{remark}1
The notions $\svdMax{\Delta_{\LMM}(\omega)}$ and the ensuing  $\widehat{\phantom{_\infty}\infnorm{\Delta_{\LMM}}}$  should be regarded as notational convenience to denote that local models are used to estimate the maximal singular value and $\Hinf{}$ norm, respectively.
In reality, there is no tangible `$\Delta_{\LMM}$' that is constructed: neighboring local models are stitched together using the `$\max$' operator.
\end{remark}
